A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-12 paper/aosgflp.tex
New Tek formatting (aosgflp.tex. Use this from now on.

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}
  \author{Eric Mittman\thanks{Department of Statistics, Iowa State University}\\
    and \\
    Colin Lewis-Beck\footnotemark[1]\\
    and \\
    William Q. Meeker\footnotemark[1]}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
When analyzing field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of failure, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate. 
Furthermore, when the information carried by lifetime data are limited by sample size, censoring and truncation, estimates can be unstable and suffer from imprecision. These limitations are typical; for example, lifetime data for high-reliability products will naturally tend to be right-censored.

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  early failures due to ``infant mortality'' and failures due to wearout. We fit the GLFP model using a hierarchical modeling approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using our Bayesian method, comparison of different product brands is straightforward because estimation of arbitrary functionals are easily computable using draws from the joint posterior distribution of the model parameters. Potential applications include assessment and comparison of reliability to inform purchasing decisions.
\end{abstract}

\noindent%
{\it Keywords:} GLFP, Bathtub hazard, Censored data, Hierarchical models, Bayesian estimation
\vfill

\newpage
\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that can accomodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

Nonparametric methods require relatively few assumptions, but they are not suitable for prediction. Moreover, nonparametric estimates made using small samples, or data which are heavily censored may be too noisy to be practical. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are well-equipped to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare populations of interest, borrow strength across groups, and incorporate prior information.

@@

Previous papers have employed various assumptions and methods to model masked lifetime failure data.  When modeling computer system failures \citet{reiser} assumed each observed failure came from a known subset of failure modes, and estimation was performed using a Bayesian approach.  \cite{chan} labeled the cause of circuit board failures as infant mortality, unknown, or wearout based on the time of observed failures.  This helped identify parameters when using maximum likelihood (ML) estimation.  Extending Chan and Meeker's analysis, \citet{basu} performed a Bayesian analysis with informative priors to better identify early versus late failure modes without making any assumptions about the cause of failure.  \cite{berger} introduced the Poly-Weibull distribution where the failure time is the minimum of a several Weibull distributions, corresponding to different failure modes.  More recently, \cite{ranjan} considered a competing risk model for infant mortality and wearout as a mixture of Weibull and exponential failure distributions.  Treating the unknown failure modes as incomplete data, an expectation maximization (EM) algorithm providing ML estimates was used, in addition to Bayesian estimation.

@@

\subsection{Weibull parameterization}
\label{sec:Weibull parameterization}
For a random variable $T$ following a Weibull distribution, the standard parameterization of the cumulative distribution function, in terms of scale parameter $\alpha$ and shape parameter $\beta$, is

$$ \Pr(T \le t) = F(t|\alpha,\beta) = 1 - \exp \left[ \left( -\frac{t}{\alpha} \right)^\beta \right]. $$

An alternative parameterization, in terms of log-location parameter $\mu = \log (\alpha)$ and log-scale parameter $\sigma = 1/\beta$ is

\begin{equation} \Pr(T \le t) = F(t|\mu, \sigma) = 1 - \exp \left\{ -\exp \left[ \frac{ \log (t) - \mu }{\sigma} \right] \right\}\\
= \Phi_{SEV}\left[\frac{\log (t) - \mu}{\sigma}\right],
\end{equation}
where $\Phi_{SEV}$ is the cdf of the standard smallest extreme value distribution (SEV). Thus, the Weibull distribution is a log-location scale family, with $\log(T)$ following an SEV distribution with location parameter $\mu$ and scale parameter $\sigma$. 
% With this in mind, the corresponding density function is
% \begin{equation}
% f(t|\mu, \sigma) =\frac{1}{\sigma t} \phi_{SEV}\left[\frac{\log(t) - \mu}{\sigma}\right]
% \end{equation}

An advantage conferred by writing the model in this way is that the log of the $p$ quantile, $t_p$, is a linear function of the parameters, namely, $\log(t_p) = \mu + \sigma \Phi_{SEV}^{-1}(p)$. This allows an analyst to apply prior information in a straightforward way. Reparameterizing in terms of $(\log(t_p),\sigma)$, we can write the Weibull cdf as
\begin{equation}
\Pr(T \le t) = F(t|\text{log}(t_p), \sigma) = \Phi_{SEV}\left[\frac{\log(\frac{t}{t_p}) + \sigma \Phi_{SEV}^{-1}(p)}{\sigma}\right]
\end{equation}
When there is more prior knowledge about a lower quantile, as is often the case with high-reliability products, using this parameterization allows the analyst to put prior distributions directly on those quantities. In addition, in the presence of censoring, $p$ can be chosen to make $\log(t_p)$ and $\sigma$ approximately independent. Since the choice of independent marginal priors is common in practice, this observation lends further credence to the use of these reparameterizations.

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\mbox{logit}^{-1}\pi \sim \op{Logitnormal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & 2.5\% & 50\% & 97.5\% \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03\times 10^3$  & $2.28 \times 10^3$ & $3.99 \times 10^3$\\ 
  $t_{0.2,2}$ & $1.80 \times 10^4$ & $1.82 \times 10^4$ & $1.86 \times 10^4$ \\ 
   \hline
\end{tabular}
\caption{Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.}
\label{table:1}
\end{table}

@@

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted K-M estimate with axes on the Weibull probability scale.  90\% pointwise uncertainty bands associated with each estimator are included. While the Weibull model is inadequate for these data, the GLFP model fits quite well, as it is able to capture the acceleration of the hazard rate between 8000 and 20,000 hours. %The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by``$T(0,1)$" above) restricting the wearout failure mode to have an increasing hazard function (e.g., $\beta_{2g} = 1/\sigma_{2g}>1$). We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

We can also compare posterior estimates of time to failure under Models 1-4 for each drive-model individually.  For these comparisons, we calculate, pointwise, the posterior median of proportion failing over a grid. That is, for every model, and for a fixed set, $\tilde{t}=\{\tilde{t}_1,\ldots,\tilde{t}_M\}$, we compute 
\begin{equation}
\label{pointwise-medians}
\op{median}\left\{\op{GLFP}\left(\tilde{t}_m|\pi_{g}^{(s)},\mu_{1g}^{(s)},\sigma_{1g}^{(s)},\mu_{2g}^{(s)},\sigma_{2g}^{(s)}\right);s=1,\ldots,S \right\},
\end{equation}
where $\theta^{(s)}$ is the $s^{th}$ posterior sample from $p(\theta|y)$.
%Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the K-M quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

@@

\begin{equation}
\mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] = \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{equation}
\noindent Using this criterion, we should choose the Model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\frac{\sum_{i=1}^S w_{i,s} p(t_{g,i})}{\sum_{s=1}^S w_{i,s}}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

@@

We can compare the 19 simulated data sets $y_{rep,g, i}$ to the observed data $y_{g,i}$ by using them to re-estimate the K-M estimator. The resulting plots are displayed in Figure \ref{fig:post-pred-KM}. Only a representative sample of plots is shown here for brevity (see the Supplementary Material for the complete set of drive-models).  For most drive-models, the estimates based on the observed data look similar to those based on the replicated data.  There are a few drive-models, however where this is not the case. Drive-model 14 shows a discrepancy between the GFLP fit and the K-M fit in the right tail. In particular, the GLFP predictions appear conservative, overpredicting the proportion failing after about 2.5 years. Due to the large number of failures for this Drive-model, the posterior for the hierarchical model is similar to the stand-alone model. Other drive-models showing a lack of fit are 4 and 34. We first address Drive-model 4; our diagnosis of 34 is analogous, so the following comments extend to that Drive-model as well.

@@

@@

\subsubsection{Drive-model comparisons}
\label{subsubsec:Drive-model comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation*}
  p(t_{d,new}|t) = \int p(t_{d,new}|\theta_d) p(\theta_d|t_d) \, d\theta_d
\end{equation*}

@@

\section{Supplementary Material}
\label{sec:supple}

\begin{description}

\item[Stan Code and Plots] Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6 (supplementary.pdf)

\item[Backblaze hard-drive data] Lifetime data set for all 44 drive-models used in our analysis. (backblaze\_hd\_data.csv)

\end{description}

>>>>

% Template for the submission to:
%   The Annals of Probability           [aop]
%   The Annals of Applied Probability   [aap]
%   The Annals of Statistics            [aos] 
%   The Annals of Applied Statistics    [aoas]
%   Stochastic Systems                  [ssy]
%
%Author: In this template, the places where you need to add information
%        (or delete line) are indicated by {???}.  Mostly the information
%        required is obvious, but some explanations are given in lines starting
%Author:
%All other lines should be ignored.  After editing, there should be
%no instances of ??? after this line.

% use option [preprint] to remove info line at bottom
% journal options: aop,aap,aos,aoas,ssy
% natbib option: authoryear
\documentclass[aoas]{imsart}
\RequirePackage{natbib}
\usepackage{amsthm,amsmath,natbib,enumerate}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url, imsart}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\bibliographystyle{imsart-nameyear}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation
% put your definitions there:
\startlocaldefs
\endlocaldefs

@@

\begin{frontmatter}

% "Title of the paper"
\title{A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}

\begin{aug}
  \author{\fnms{Eric}  \snm{Mittman}\corref{}\ead[label=e1]{first@somewhere.com}},
  \author{\fnms{Colin} \snm{Lewis-Beck}\ead[label=e2]{second@somewhere.com}}
  \and
  \author{\fnms{William Q.}  \snm{Meeker}%
  \ead[label=e3]{third@somewhere.com}%
  \ead[label=u1,url]{http://www.foo.com}}

  %\thankstext{t2}{Footnote to the first author with the `thankstext' command.}

  %\runauthor{F. Author et al.}

  \affiliation{Iowa State University}

  \address{Address of the First and Second authors,\\ 
          \printead{e1,e2}}

  \address{Address of the Third author,\\
          \printead{e3,u1}}

\end{aug}

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
%\author{\fnms{Eric Mittman and Colin Lewis-Beck and William Q. Meeker}}
%\affiliation{Iowa State University}
%\address{\printead{e1}}
%\and
%\author{\fnms{???} \snm{???}\ead[label=e2]{???}}
%\address{\printead{e2}}
%\affiliation{???}

%\runauthor{???}

\begin{abstract}
When analyzing field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of failure, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate. 
Furthermore, when the information carried by lifetime data are limited by sample size, censoring and truncation, estimates can be unstable and suffer from imprecision. These limitations are typical; for example, lifetime data for high-reliability products will naturally tend to be right-censored.

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  early failures due to ``infant mortality'' and failures due to wearout. We fit the GLFP model using a hierarchical modeling approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using our Bayesian method, comparison of different product brands is straightforward because estimation of arbitrary functionals are easily computable using draws from the joint posterior distribution of the model parameters. Potential applications include assessment and comparison of reliability to inform purchasing decisions.

\end{abstract}

%\begin{keyword}[class=MSC]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\begin{keyword}
\kwd{GLFP, Bathtub hazard, Censored data, Hierarchical models, Bayesian estimation}
%\kwd{}
\end{keyword}

\end{frontmatter}

\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that can accomodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

Nonparametric methods require relatively few assumptions, but they are not suitable for prediction. Moreover, nonparametric estimates made using small samples, or data which are heavily censored may be too noisy to be useful. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are well-equipped to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare populations of interest, borrow strength across groups, and incorporate prior information.

@@

Previous papers have employed various assumptions and methods to model masked lifetime failure data.  When modeling computer system failures \citet{reiser} assumed each observed failure came from a known subset of failure modes, and estimation was performed using a Bayesian approach.  \cite{chan} labeled the cause of circuit board failures as infant mortality, unknown, or wearout based on the time of observed failures.  This helped identify parameters when using maximum likelihood (ML) estimation.  Extending Chan and Meeker's analysis, \citet{basu} performed a Bayesian analysis with informative priors to better identify early versus late failure modes without making any assumptions about the cause of failure.  \cite{berger} introduced the Poly-Weibull distribution where the failure time is the minimum of a several Weibull distributions, corresponding to different failure modes.  \cite{ranjan} considered a competing risk model for infant mortality and wearout as a mixture of Weibull and exponential failure distributions.  Treating the unknown failure modes as incomplete data, an expectation maximization (EM) algorithm providing ML estimates was used, in addition to Bayesian estimation.

@@

\subsection{Weibull parameterization}
\label{sec:Weibull parameterization}
The Weibull cumulative
 distribution function (cdf) is
\begin{align}
\label{equation:weibull.cdf}
\Pr(T \leq t|\alpha,\beta ) &= F(t|\alpha,\beta)=1-
\exp \left [-\left (\frac{t}{\alpha} \right )^{\beta}
\right ], \quad t > 0,
\end{align}
where $\beta>0$ is the Weibull shape parameter and $\alpha>0$ is a
scale parameter. Because $\log(T)$ has a smallest extreme value
distribution (a member of the location-scale family of
distributions), the Weibull cdf can also be written as
\begin{align*}
\Pr(T \leq t| \mu,\sigma ) &= F(t| \mu,\sigma)= \Phi_{SEV}\left[\frac{\log(t)-\mu}{\sigma}\right], \quad t > 0,
\end{align*}
where $\Phi_{SEV}(z)=1-\exp[-\exp(z)]$ is the standard smallest extreme value
distribution cdf and
$\mu=\log(\alpha)$ and $\sigma=1/\beta$ are, respectively, location
and scale parameters for the distribution of $\log(T)$. Thus the Weibull
distribution is a member of the log-location-scale family of
distributions.

For purposes of specifying a prior distribution for the Weibull
distribution parameters, we will use an alternative parameterization
where $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{1/\beta}$. Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{1/\beta}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\beta ) = F(t|t_{p},\beta)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{1/\beta}} \right )^{\beta}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{\beta}\right], \quad t > 0.
\end{align*}
There are two important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$. There is, however, generally available
information the shape parameter $\beta$ for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, the
it is known that $\beta>1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\alpha$ and $\beta$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\beta$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\%
failing, then choosing $t_{0.05}$ would 
work well.
\end{itemize}

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\mbox{logit}^{-1}\pi \sim \op{Logitnormal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\beta_1, \beta_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 7.7 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & 2.5\% & 50\% & 97.5\% \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03\times 10^3$  & $2.28 \times 10^3$ & $3.99 \times 10^3$\\ 
  $t_{0.2,2}$ & $1.80 \times 10^4$ & $1.82 \times 10^4$ & $1.86 \times 10^4$ \\ 
   \hline
\end{tabular}
\caption{Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.}
\label{table:1}
\end{table}

@@

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted K-M estimate with axes on the Weibull probability scale.  The plot also contains 90\% pointwise uncertainty bands associated with each estimate. While the Weibull model is inadequate for these data, the GLFP model fits quite well, as it is able to capture the acceleration of the hazard rate between 8000 and 20,000 hours. %The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of log quantile and scale since the data we encounter are more informative about the left side of their respective lifetime distribution. We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by $T(0,1)$ above) restricting the wearout failure mode to have an increasing hazard function (e.g., $\beta_{2g} = 1/\sigma_{2g}>1$). We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

We can also compare posterior estimates of time to failure under Models 1-4 for each drive-model individually.  For these comparisons, we calculate, pointwise, the posterior median of the proportion failing over a grid. That is, for every model, and for a fixed set, $\tilde{t}=\{\tilde{t}_1,\ldots,\tilde{t}_M\}$, we compute 
\begin{equation}
\label{pointwise-medians}
\op{median}\left\{\op{GLFP}\left(\tilde{t}_m|\pi_{g}^{(s)},\mu_{1g}^{(s)},\sigma_{1g}^{(s)},\mu_{2g}^{(s)},\sigma_{2g}^{(s)}\right);s=1,\ldots,S \right\},
\end{equation}
where $\theta^{(s)}$ is the $s^{th}$ posterior sample from $p(\theta|y)$.
%Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

For Drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for Drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the K-M quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for Drive-model 40.

@@

\begin{equation}
\mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] = \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{equation}
\noindent Using this criterion, we should choose the model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Notationally suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\sum_{i=1}^S w_{i,s} p(t_{g,i})/\sum_{s=1}^S w_{i,s}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  
Results showing estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
 We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

@@

We can compare the 19 simulated data sets $y_{rep,g, i}$ to the observed data $y_{g,i}$ by using them to re-estimate the K-M estimator. The resulting plots are displayed in Figure \ref{fig:post-pred-KM}. Only a representative sample of plots is shown here for brevity (see the Supplementary Material for similar plots for all of the drive-models).  For most drive-models, the estimates based on the observed data look similar to those based on the replicated data.  There are a few drive-models, however where this is not the case. Drive-model 14 shows a discrepancy between the GFLP fit and the K-M fit in the right tail. In particular, the GLFP predictions appear conservative, overpredicting the proportion failing after about 2.5 years. Due to the large number of failures for this Drive-model, the posterior for the hierarchical model is similar to the stand-alone model. Other drive-models showing a lack of fit are 4 and 34. We first address Drive-model 4; our diagnosis of 34 is analogous, so the following comments extend to that drive-model as well.

@@

A possible explanation for the discrepancy shown in Figure 7 is that
the units of Drive-model 4 were introduced into the field over a
period of xx months. Manufactures of hard drives (and most other
products) often make changes to the product design over time to
either improve reliability or to reduce cost. Such changes will
sometimes have an important effect on the products failure-time
distribution, invalidating one of our important assumptions that
failure-time distribution for a drive-model does not depend on the
date of manufacture.

@@

\subsubsection{Drive-model comparisons}
\label{subsubsec:Drive-model comparisons}
We consider the problem of ranking drive-models with respect to economical value. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

There are two sources of variation at play: the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation*}
  p(t_{d,new}|t) = \int p(t_{d,new}|\theta_d) p(\theta_d|t_d) \, d\theta_d
\end{equation*}

@@

\section{Online Supplementary Material}
\label{sec:supple}
\begin{supplement}[id=suppA]
  \sname{Supplement A}
  \stitle{Stan Code and Plots}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.pdf}
  \sdescription{Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6.}
\end{supplement}
